### 2014-01-05 inst/doc/Advanced_writing_of_EML.Rmd
troubleshooting various minor bugs arising from recent changes not caught earlier. Avoid warnings from collate list, validation errors from missing contact when only creator config provided, tweaks to publish_knb().  Still need some tweaks to eml_read to handle identifiers directly.  Still testing on tutorials and vignettes.

```{r}
dat <- read.csv(system.file("examples", "hf205-01-TPexp1.csv", package="reml"), colClasses = 
                  c("factor", "Date", "Date", "Date", "factor", "factor", "factor"))
```

@@

Yet another way to create person objects is to use the helper function `eml_person`.  This function recongnizes the plain-text string conventions already used by R's person objects (or the person objects themselves, see ?person).   Here we add other researchers as contributors to the data.  The `eml_person` function automatically decides whether to return a `contact`, `creator` list, or `associatedParty`, based on the additional information provided (such as an email address in angle braces, contributor role in square brackets).

```{r}
other_researchers <- eml_person("Benjamin Baiser [ctb]", "Jennifer Sirota [ctb]") # creates a 'ListOfassociatedParty' (roles != cre)
```

@@

```{r}
keys <- eml_keyword(list("LTER controlled vocabulary" = c("bacteria", "carnivorous plants", "genetics", "thresholds"),
                                     "LTER core area" = c("populations", "inorganic nutrients", "disturbance"),
                                        "HFR default" = c("Harvard Forest", "HFR", "LTER", "USA")))
```

A similar situation arises with describing the coverage metadata element. 
```{r}
coverage <- eml_coverage(scientific_names = "Sarracenia purpurea", 
                         dates            = c('2012-06-01', '2013-12-31'),
                         geographic_description = "Harvard Forest Greenhouse, Tom Swamp Tract (Harvard Forest)", 
                         NSEWbox          = c( 42.55,  42.42, -72.1, -72.29, 160, 330))
```

>>>>

```{r}
f <- system.file("examples", "hf205-01-TPexp1.csv", package="reml")
dat <- read.csv(f, 
                colClasses = "factor", # c("factor", "Date", "Date", "Date", 
                             #  "factor", "factor", "factor")
                )
```

@@

Yet another way to create person objects is to use the helper function `eml_person`.  This function recongnizes the plain-text string conventions already used by R's person objects (or the person objects themselves, see ?person).   Here we add other researchers as contributors to the data.  The `eml_person` function automatically decides whether to return a `contact`, `creator` list, or `associatedParty`, based on the additional information provided (such as an email address in angle braces, contributor role, `ctb` in square brackets).

```{r}
other_researchers <- eml_person("Benjamin Baiser [ctb]", 
                                "Jennifer Sirota [ctb]") 
```

@@

```{r}
keys <- eml_keyword(list(
 "LTER controlled vocabulary" = c("bacteria", 
                                  "carnivorous plants", 
                                  "genetics", 
                                  "thresholds"),
             "LTER core area" = c("populations", 
                                  "inorganic nutrients", 
                                  "disturbance"),
                "HFR default" = c("Harvard Forest", 
                                  "HFR", 
                                  "LTER", 
                                  "USA")))
```

A similar situation arises with describing the coverage metadata element. 
```{r}
coverage <- eml_coverage(
  scientific_names = "Sarracenia purpurea", 
  dates            = c('2012-06-01', '2013-12-31'),
  geographic_description = "Harvard Forest Greenhouse, 
                            Tom Swamp Tract (Harvard Forest)", 
  NSEWbox          = c( 42.55,  42.42, -72.1, -72.29, 160, 330))
```

### 2014-01-05 inst/doc/README.Rmd
tweak default field values after simplifying eml_write workflow, tests pass with validation
troubleshooting various minor bugs arising from recent changes not caught earlier. Avoid warnings from collate list, validation errors from missing contact when only creator config provided, tweaks to publish_knb().  Still need some tweaks to eml_read to handle identifiers directly.  Still testing on tutorials and vignettes.

```{r include=FALSE, cache=FALSE}
source("~/.knitr_defaults.R")
opts_chunk$set(cache=FALSE)
```

@@

```{r publish_knb, eval=FALSE}
eml_publish("reml_example.xml", destination="KNB", permanent=FALSE)
```

@@

>>>>

```{r include=FALSE, cache=FALSE}
source("~/.knitr_defaults.R")
```

@@

```{r publish_knb, eval=FALSE}
ids <- eml_publish("reml_example.xml", destination="KNB", permanent=FALSE)
```

@@

<!--
Test data shows up on the test server, followed by the identifer, at `paste0("(https://mn-demo-5.test.dataone.org/knb/d1/mn/v1/object/", ids[["eml"]])`

This returns the object identifiers for the EML metadata, the csv file, and the package itself.  We can read in the EML directly from its unique identifier using `eml_read`. We must wait about four minutes first for the entry to be completely registered in the dataone repository.  (Note that because we are using the development server, `permanent=FALSE`, this file will dissapear after a few days.)

```{r}
Sys.sleep(60*4)
eml <- eml_read(paste0("(https://mn-demo-5.test.dataone.org/knb/d1/mn/v1/object/", ids[["eml"]]))
```
-->
